### 2024-03-28 paper/paper.qmd
try

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Harrison Huang
thanks: "Code and data are available at: LINK."
date: today 
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-03-28 scripts/01-download_data.R

@@ -15,7 +15,8 @@ library(tidyverse)
 
 #### Download data ####
 
-
+politics_datasets <-
+  fromJSON("https://demo.dataverse.org/api/search?q=politics")
 
 
 #### Save data ####

### 2024-04-04 paper/paper.qmd
download data

@@
 ---
-title: "My title"
+title: "Performance of Rookie Can Predict Price of Their RC based Prizm Cards"
 subtitle: "My subtitle if needed"

### 2024-04-04 scripts/01-download_data.R

@@ -11,17 +11,48 @@
 #### Workspace setup ####
 library(opendatatoronto)
 library(tidyverse)
-
+library(arrow)
 
 #### Download data ####
 
-politics_datasets <-
-  fromJSON("https://demo.dataverse.org/api/search?q=politics")
+
+# All players data
+all_player_datasets <-
+  fromJSON("https://api.sportsdata.io/v3/nba/scores/json/Players?key=92a4662dc81b4f56bd99cc606f483004")
+
+
+#Zion Williamson's data set
+Zion_datasets <-
+  fromJSON("https://api.sportsdata.io/v3/nba/stats/json/PlayerGameStatsBySeason/2023/20002271/all?key=92a4662dc81b4f56bd99cc606f483004")
+
+#Anthony Edwards's data set
+Anthony_datasets <-
+  fromJSON("https://api.sportsdata.io/v3/nba/stats/json/PlayerGameStatsBySeason/2023/20002523/all?key=92a4662dc81b4f56bd99cc606f483004")
+
+#Lamelo Ball data set
+LaMelo_datasets <-
+  fromJSON("https://api.sportsdata.io/v3/nba/stats/json/PlayerGameStatsBySeason/2023/20002528/all?key=92a4662dc81b4f56bd99cc606f483004")
+
+#Tyrese Haliburton
+Haliburton_datasets <-
+  fromJSON("https://api.sportsdata.io/v3/nba/stats/json/PlayerGameStatsBySeason/2023/20002537/all?key=92a4662dc81b4f56bd99cc606f483004")
+
+#Tyrese Maxey
+maxey_datasets <-
+  fromJSON("https://api.sportsdata.io/v3/nba/stats/json/PlayerGameStatsBySeason/2023/20002546/all?key=92a4662dc81b4f56bd99cc606f483004")
+
 
 
 #### Save data ####
 
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
 
+write_csv(all_player_datasets, "data/raw_data/raw_all_player_datasets.csv")
+
+write_csv(Zion_datasets, "data/raw_data/raw_zion_datasets.csv")
+
+write_csv(LaMelo_datasets, "data/raw_data/raw_lamelo_datasets.csv")
+
+write_csv(Haliburton_datasets, "data/raw_data/raw_haliburton_datasets.csv")
+
+write_csv(maxey_datasets, "data/raw_data/raw_maxey_datasets.csv")
          

### 2024-04-04 paper/paper.qmd
save data as csv

--- 2024-03-28 paper/paper.qmd
@@
   - Harrison Huang
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/lemonface88/NBA"
 date: today 
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Collecting and investing in cards has been relevant for a while now.
+There are complex factors that contribute to the price fluxation of these cards.
+This analysis will use player statistics to create a model to try to grasp possible future price trends of the card.
+A xxx model was used in this analysis.
+The results indicated that xxx is a strong indicator of the price fluctuation of potential future prices of the rookie card."
 format: pdf
@@
 ---
+
+# Introduction
+
+Collectible cards such as Pokemon, Yu-Gi-Oh!
+cards, and Sports cards still exist and are relevant in our world.
+In the digitized world we live in today, these physical cards are often forgotten.
+We have also heard wild stories about specific Pokemon cards selling for millions of dollars, the same applies to other collectible cards.
+NBA basketball cards have gained significant popularity in recent years.
+Apart from being collector's items, they have also become a form of investment for some individuals.
+
+Many factors go into the valuation of a basketball card.
+Some example factors include the rarity of the card, the performance and popularity of the player, which series it comes from, and the condition of the card.
+Each year, the cards are updated and RC labeled cards are labeled on the players that are rookies for that year.
+These RC-labeled cards are only printed in that specific year and are usually the most sought-after cards among collectors.
+The specific stats of each player such as points per game, rebounds, and turnover also dictate the valuation of their rookie cards.
+The complexity of these elements often makes it difficult to predict the future value of the card.
+
+This analysis finds that….
+
+	In Section 2 of the paper, the source and datasets are discussed.
+Strengths and weaknesses, methods of collection, and terminologies will be explored.
+Section 3 of the paper will incorporate a model aiming to use player statistics to predict the price trend of the card.
+Section 4 will then look at the results from the model.
+Lastly, section 5 will be a reflection about possible steps and the discussion of the strengths and weaknesses of this analysis.
 
@@
 
-# Introduction
-
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
-
-The remainder of this paper is structured as follows. @sec-data....
-
-# Data {#sec-data}
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+# Data
 
@@
 The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
+# Appendix
 

### 2024-04-04 scripts/02-data_cleaning.R

@@ -1,44 +1,38 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Clean out coluns with uneeded data
+# Author: Harrison Huang
+# Date: 6 April 2024
+# Contact: harri.huang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+
+
 
 #### Workspace setup ####
 library(tidyverse)
+library(janitor)
+library(tidyr)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+
+# clean zion data
+raw_data_zion <- read_csv("data/raw_data/raw_zion_datasets.csv")
+
+clean_zion_data <-
+  raw_data_zion |>
+  janitor::clean_names()|>
+  tidyr::drop_na()|>
+  
+  
+
+
+
[…]

### 2024-04-04 paper/paper.qmd
rendering the paper

@@
 
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
-
-Talk way more about it.
+Talk more about it. Data used here are unmanipulated data, simply created by graph functions with the data sets.
 
@@
 
-Our results are summarized in @tbl-modelresults.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
-
 # Discussion

### 2024-04-04 scripts/02-data_cleaning.R
cleaned data

@@ -6,33 +6,54 @@
 # License: MIT
 
 
-
 #### Workspace setup ####
 library(tidyverse)
 library(janitor)
 library(tidyr)
+library(arrow)
 
 #### Clean data ####
 
+#  janitor::clean_names()|>
+#  tidyr::drop_na()|>
 
 # clean zion data
 raw_data_zion <- read_csv("data/raw_data/raw_zion_datasets.csv")
 
 clean_zion_data <-
   raw_data_zion |>
-  janitor::clean_names()|>
-  tidyr::drop_na()|>
+  select(Day, FieldGoalsMade, FieldGoalsAttempted,FieldGoalsPercentage, TwoPointersPercentage, ThreePointersPercentage, FreeThrowsPercentage, Minutes)|>
+  filter(Minutes > 0)
   
-  
 
-
-
+# clean haliburton data
 raw_data_haliburton <- read_csv("data/raw_data/raw_haliburton_datasets.csv")
 
+clean_haliburton_data <-
+  raw_data_haliburton |>
+  select(Day, FieldGoalsMade, FieldGoalsAttempted,FieldGoalsPercentage, TwoPointersPercentage, ThreePointersPercentage, FreeThrowsPercentage, Minutes)|>
+  filter(Minutes > 0)
+
+# clean lamelo data
 raw_data_lamelo <- read_csv("data/raw_data/raw_lamelo_datasets.csv")
 
+clean_lamelo_data <-
+  raw_data_lamelo |>
+  select(Day, FieldGoalsMade, FieldGoalsAttempted,FieldGoalsPercentage, TwoPointersPercentage, ThreePointersPercentage, FreeThrowsPercentage, Minutes)|>
+  filter(Minutes > 0)
+
+
+# clean maxey data
 raw_data_maxey <- read_csv("data/raw_data/raw_maxey_datasets.csv")
+
+clean_maxey_data <-
+  raw_data_maxey |>
+  select(Day, FieldGoalsMade, FieldGoalsAttempted,FieldGoalsPercentage, TwoPointersPercentage, ThreePointersPercentage, FreeThrowsPercentage, Minutes)|>
+  filter(Minutes > 0)
 
 
 #### Save data ####
-write_csv(cleaned_data, "outputs/data/analysis_data.csv")
+write_parquet(clean_zion_data, "data/analysis_data/clean_zion_data.parquet")
+
+
+

### 2024-04-21 paper/paper.qmd
saved clean data files

@@
 ---
-title: "Performance of Rookie Can Predict Price of Their RC based Prizm Cards"
+title: "Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards"
 subtitle: "My subtitle if needed"

### 2024-04-21 scripts/00-simulate_data.R

@@ -1,19 +1,18 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates player data
+# Author: Harrison
+# Date: April 20, 2024
+# Contact: Harri.huang@mail.utornto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+
 
 
 

### 2024-04-21 scripts/02-data_cleaning.R

@@ -53,7 +53,6 @@ clean_maxey_data <-
 
 
 #### Save data ####
-write_parquet(clean_zion_data, "data/analysis_data/clean_zion_data.parquet")
 
 
 

### 2024-04-21 scripts/03-test_data.R

@@ -1,15 +1,14 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests data
+# Author: Harrison Huang
+# Date: April 20, 2024
+# Contact: Harri.huang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Test data ####

### 2024-04-21 scripts/00-simulate_data.R
fine tune

@@ -13,6 +13,6 @@ library(tidyverse)
 
 #### Simulate data ####
 
-
+set.seed(888)
 
 

### 2024-04-21 scripts/02-data_cleaning.R

@@ -55,4 +55,13 @@ clean_maxey_data <-
 #### Save data ####
 
 
+# becase of errors that occur throughout the attemts to save files as  parquet, the files will not be saved as parquet format. 
+#Error in parquet___WriterProperties___Builder__create() : 
+#Cannot call parquet___WriterProperties___Builder__create(). See https://arrow.apache.org/docs/r/articles/install.html for help installing Arrow C++ libraries. 
+
+
+write_csv(clean_zion_data, "data/analysis_data/cleaned_zion_data.csv")
+write_csv(clean_lamelo_data, "data/analysis_data/cleaned_lamelo_data.csv")
+write_csv(clean_maxey_data, "data/analysis_data/cleaned_maxey_data.csv")
+write_csv(clean_haliburton_data, "data/analysis_data/cleaned_haliburton_data.csv")
 

### 2024-04-21 scripts/03-test_data.R

@@ -4,7 +4,8 @@
 # Date: April 20, 2024
 # Contact: Harri.huang@mail.utoronto.ca
 # License: MIT
-
+# Pre-requisites: run 01-download_data.R and 02-data_cleaning.R
+# Any other information needed? If nothing is printed, all tests have passed
 
 
 #### Workspace setup ####

### 2024-04-21 scripts/01-download_data.R
obtained new data from ESPN

@@ -9,50 +9,37 @@
 
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
-library(arrow)
+library(rvest)
+library(stringr)
+library(dplyr)
 
 #### Download data ####
 
+# Data for maxey during 2024-2024 split
+maxey_url_2023 <- read_html("https://www.espn.com/nba/player/splits/_/id/4431678/tyrese-maxey")
 
-# All players data
-all_player_datasets <-
-  fromJSON("https://api.sportsdata.io/v3/nba/scores/json/Players?key=92a4662dc81b4f56bd99cc606f483004")
+maxey_tables <- 
+  maxey_url_2023 |>
+  html_nodes("table")|>
+  html_table(fill = TRUE)
 
+# the big table on the ESPN website is actually split in half, therefore we need to merge it back after scraping it
+maxey_left <- maxey_tables[[1]]
+maxey_right <- maxey_tables[[2]]
 
-#Zion Williamson's data set
-Zion_datasets <-
-  fromJSON("https://api.sportsdata.io/v3/nba/stats/json/PlayerGameStatsBySeason/2023/20002271/all?key=92a4662dc81b4f56bd99cc606f483004")
-
-#Anthony Edwards's data set
-Anthony_datasets <-
-  fromJSON("https://api.sportsdata.io/v3/nba/stats/json/PlayerGameStatsBySeason/2023/20002523/all?key=92a4662dc81b4f56bd99cc606f483004")
-
-#Lamelo Ball data set
-LaMelo_datasets <-
-  fromJSON("https://api.sportsdata.io/v3/nba/stats/json/PlayerGameStatsBySeason/2023/20002528/all?key=92a4662dc81b4f56bd99cc606f483004")
-
-#Tyrese Haliburton
-Haliburton_datasets <-
-  fromJSON("https://api.sportsdata.io/v3/nba/stats/json/PlayerGameStatsBySeason/2023/20002537/all?key=92a4662dc81b4f56bd99cc606f483004")
-
-#Tyrese Maxey
-maxey_datasets <-
-  fromJSON("https://api.sportsdata.io/v3/nba/stats/json/PlayerGameStatsBySeason/2023/20002546/all?key=92a4662dc81b4f56bd99cc606f483004")
+maxey_data_c <-
+cbind(maxey_left, maxey_right)
 
 
+view(maxey_data_c)
+
+# Data for maxey during 2024-2024 split
 
[…]

### 2024-04-21 scripts/03-test_data.R

@@ -10,6 +10,59 @@
 
 #### Workspace setup ####
 library(tidyverse)
-
+library(dplyr)
+library(janitor)
 
 #### Test data ####
+
+
+# read cleaned player data
+
+test_zion_data = read_csv(
+  file = "data/analysis_data/cleaned_zion_data.csv",
+  show_col_types = FALSE
+)
+
+test_lamelo_data = read_csv(
+  file = "data/analysis_data/cleaned_maxey_data.csv",
+  show_col_types = FALSE
+)
+
+test_haliburton_data = read_csv(
+  file = "data/analysis_data/cleaned_lamelo_data.csv",
+  show_col_types = FALSE
+)
+
+test_maxey_data = read_csv(
+  file = "data/analysis_data/cleaned_haliburton_data.csv",
+  show_col_types = FALSE
+)
+
+
+
+### Test the data above ###
+
+# Test zion data #
+if (min(test_zion_data$Minutes) < 1) {
+  print("Game when player did not play detected")
+}
+
+if (max(test_zion_data$Minutes) > 48) {
+  print("Player played more than max possible time")
+}
+
+if (min(test_youth_data$ticket_count) < 0) {
+  print("Negative number in ticket count")
+}
+
+if (min(test_youth_data$ticket_count) < 0) {
+  print("Negative number in ticket count")
+}
+
+if (min(test_youth_data$ticket_count) < 0) {
+  print("Negative number in ticket count")
+}
+
+# Test lamelo data #
+
+# Test lamelo data #

### 2024-04-21 scripts/00-simulate_data.R
added basic simulated data

@@ -16,3 +16,25 @@ library(tidyverse)
 set.seed(888)
 
 
+simulated_player_data <-
+  tibble(
+    # randomly select a year to assign to the ticket_count
+    offence_year = sample(
+      x = c("October", "November", "December", "January", "Feburary", "March", "April"),
+      size = 1000,
+      replace = TRUE
+    ), 
+    
+    # randomly assigning each player to a month
+    age_group =  sample(
+      x = c("LaMelo Ball", "Tyrese Maxey", "Tyrese Haliburton", "Zion Williamson", "Edward Anthony"),
+      size = 1000,
+      replace = TRUE),
+    
+    # statistics of points per game
+    pps = sample(
+      x = c(0:60),
+      size = 1000,
+      replace = TRUE)
+  )
+

### 2024-04-21 scripts/00-simulate_data.R
finished simulating data

@@ -32,9 +32,37 @@ simulated_player_data <-
       replace = TRUE),
     
     # statistics of points per game
-    pps = sample(
-      x = c(0:60),
+    ppg = sample(
+      x = c(round(0:500/10, digits = 1)),
+      size = 1000,
+      replace = TRUE),
+    
+    # statistics of assist per game 
+    ast = sample(
+      x = c(round(0:70/10, digits = 1)),
+      size = 1000,
+      replace = TRUE),
+    
+    # statistics of blocks per game
+    blk = sample(
+      x = c(round(0:10/10, digits = 1)),
+      size = 1000,
+      replace = TRUE),
+    
+    
+    # statistics of rebound per game
+    reb = sample(
+      x = c(round(0:70/10, digits = 1)),
+      size = 1000,
+      replace = TRUE),
+    
+    
+    # statistics of steals per game
+    stl = sample(
+      x = c(round(0:20/10, digits = 1)),
       size = 1000,
       replace = TRUE)
+    
   )
 
+view(simulated_player_data)

### 2024-04-21 scripts/01-download_data.R
addded haliburton and maxey raw data

@@ -16,7 +16,24 @@ library(dplyr)
 
 #### Download data ####
 
-# Data for maxey during 2024-2024 split
+# Data for maxey during 2022-2023 split
+maxey_url_2022 <- read_html("https://www.espn.com/nba/player/splits/_/id/4431678/type/nba/year/2023/category/perGame")
+
+maxey_tables <- 
+  maxey_url_2022 |>
+  html_nodes("table")|>
+  html_table(fill = TRUE)
+
+# the big table on the ESPN website is actually split in half, therefore we need to merge it back after scraping it
+maxey_left <- maxey_tables[[1]]
+maxey_right <- maxey_tables[[2]]
+
+maxey_data_2022 <-
+  cbind(maxey_left, maxey_right)
+
+view(maxey_data_2022)
+# Data for maxey during 2023-2024 split
+
 maxey_url_2023 <- read_html("https://www.espn.com/nba/player/splits/_/id/4431678/tyrese-maxey")
 
 maxey_tables <- 
@@ -28,18 +45,73 @@ maxey_tables <-
 maxey_left <- maxey_tables[[1]]
 maxey_right <- maxey_tables[[2]]
 
-maxey_data_c <-
+maxey_data_2023 <-
 cbind(maxey_left, maxey_right)
-
 
 view(maxey_data_c)
 
-# Data for maxey during 2024-2024 split
+
+# Data for haliburton during 2022-2023 split
+haliburton_url_2022 <- read_html("https://www.espn.com/nba/player/splits/_/id/4396993/type/nba/year/2023/category/perGame")
+
+haliburton_tables <- 
+  haliburton_url_2022 |>
+  html_nodes("table")|>
+  html_table(fill = TRUE)
+
+# the big table on the ESPN website is actually split in half, therefore we need to merge it back after scraping it
+haliburton_left <- haliburton_tables[[1]]
+haliburton_right <- haliburton_tables[[2]]
+
+haliburton_data_2022 <-
+  cbind(haliburton_left, haliburton_right)
+
+# Data for haliburton during 2023-2024 split
+haliburton_url_2023 <- read_html("https://www.espn.com/nba/player/splits/_/id/4396993/type/nba/year/2024/category/perGame")
+
+haliburton_tables <- 
+  haliburton_url_2023 |>
+  html_nodes("table")|>
+  html_table(fill = TRUE)
+
[…]

### 2024-04-22 scripts/01-download_data.R
download data

@@ -78,28 +78,104 @@ haliburton_tables <-
 haliburton_left <- haliburton_tables[[1]]
 haliburton_right <- haliburton_tables[[2]]
 
-haliburton_data_2022 <-
+haliburton_data_2023 <-
   cbind(haliburton_left, haliburton_right)
 
 
 
-# Data for zion during 2022-2023 split
+# Data for zion williamson during 2022-2023 split
+zion_url_2022 <- read_html("https://www.espn.com/nba/player/splits/_/id/4395628/type/nba/year/2023/category/perGame")
 
-# Data for zion during 2023-2024 split
+zion_tables <- 
+  zion_url_2022 |>
+  html_nodes("table")|>
+  html_table(fill = TRUE)
 
+# the big table on the ESPN website is actually split in half, therefore we need to merge it back after scraping it
+zion_left <- zion_tables[[1]]
+zion_right <- zion_tables[[2]]
+
+zion_data_2022 <-
+  cbind(zion_left, zion_right)
+
+# Data for zion williamson during 2023-2024 split
+zion_url_2023 <- read_html("https://www.espn.com/nba/player/splits/_/id/4395628/type/nba/year/2024/category/perGame")
+
+zion_tables <- 
+  zion_url_2023 |>
+  html_nodes("table")|>
+  html_table(fill = TRUE)
+
+# the big table on the ESPN website is actually split in half, therefore we need to merge it back after scraping it
+zion_left <- zion_tables[[1]]
+zion_right <- zion_tables[[2]]
+
+zion_data_2023 <-
+  cbind(zion_left, zion_right)
 
 
 # Data for anthony edward during 2022-2023 split
+anthony_edward_url_2022 <- read_html("https://www.espn.com/nba/player/splits/_/id/4594268/type/nba/year/2023/category/perGame")
+
+anthony_edward_tables <- 
+  anthony_edward_url_2022 |>
+  html_nodes("table")|>
+  html_table(fill = TRUE)
+
+# the big table on the ESPN website is actually split in half, therefore we need to merge it back after scraping it
+anthony_edward_left <- anthony_edward_tables[[1]]
+anthony_edward_right <- anthony_edward_tables[[2]]
+
+anthony_edward_data_2022 <-
+  cbind(anthony_edward_left, anthony_edward_right)
 
 # Data for anthony edward 2023-2024 split
[…]

### 2024-04-22 scripts/00-simulate_data.R
added simulated data

@@ -26,7 +26,7 @@ simulated_player_data <-
     ), 
     
     # randomly assigning each player to a month
-    age_group =  sample(
+    player_name =  sample(
       x = c("LaMelo Ball", "Tyrese Maxey", "Tyrese Haliburton", "Zion Williamson", "Edward Anthony"),
       size = 1000,
       replace = TRUE),
@@ -65,4 +65,38 @@ simulated_player_data <-
     
   )
 
-view(simulated_player_data)
+
+##Simulate Player Card Price data##
+
+simulated_price_data <-
+  tibble(
+    # randomly select a year to assign to the ticket_count
+    month_of_season = sample(
+      x = c("October", "November", "December", "January", "Feburary", "March", "April"),
+      size = 1000,
+      replace = TRUE
+    ), 
+    
+    # randomly assigning each player to a month
+    player_name =  sample(
+      x = c("LaMelo Ball", "Tyrese Maxey", "Tyrese Haliburton", "Zion Williamson", "Edward Anthony"),
+      size = 1000,
+      replace = TRUE),
+    
+    # assign random price to month and person
+    
+    price =  sample(
+      x = c(round(500:1000/3, digits = 2)),
+      size = 1000,
+      replace = TRUE),
+
+  )
+
+# Example of simulated player#
+simulated_lamelo_price <-
+  simulated_price_data|>
+  filter(player_name =="LaMelo Ball")|>
+  summarise(average_price = mean(price),
+            .by = month_of_season) 
+
+

### 2024-04-22 scripts/01-download_data.R

@@ -13,7 +13,7 @@ library(tidyverse)
 library(rvest)
 library(stringr)
 library(dplyr)
-
+library(readxl)
 #### Download data ####
 
 # Data for maxey during 2022-2023 split
@@ -178,7 +178,10 @@ lamelo_data_2023 <-
   cbind(lamelo_left, lamelo_right)
 
 
+##Importing the Price data##
 
+card_price <- read_excel("~/Downloads/Card Price.xlsx")
+View(Card_Price) 
 
 #### Save data ####
 
@@ -196,3 +199,5 @@ write_csv(anthony_edward_data_2023, "data/raw_data/anthony_edward_data_2023.csv"
 
 write_csv(lamelo_data_2022, "data/raw_data/lamelo_data_2022.csv")
 write_csv(lamelo_data_2023, "data/raw_data/lamelo_data_2023.csv")
+
+write_csv(card_price, "data/raw_data/card_price.csv")

### 2024-04-22 scripts/02-data_cleaning.R

@@ -17,43 +17,36 @@ library(arrow)
 #  janitor::clean_names()|>
 #  tidyr::drop_na()|>
 
-# clean zion data
-raw_data_zion <- read_csv("data/raw_data/raw_zion_datasets.csv")
-
-clean_zion_data <-
-  raw_data_zion |>
-  select(Day, FieldGoalsMade, FieldGoalsAttempted,FieldGoalsPercentage, TwoPointersPercentage, ThreePointersPercentage, FreeThrowsPercentage, Minutes)|>
-  filter(Minutes > 0)
-  
-
-# clean haliburton data
-raw_data_haliburton <- read_csv("data/raw_data/raw_haliburton_datasets.csv")
-
-clean_haliburton_data <-
-  raw_data_haliburton |>
-  select(Day, FieldGoalsMade, FieldGoalsAttempted,FieldGoalsPercentage, TwoPointersPercentage, ThreePointersPercentage, FreeThrowsPercentage, Minutes)|>
-  filter(Minutes > 0)
-
-# clean lamelo data
-raw_data_lamelo <- read_csv("data/raw_data/raw_lamelo_datasets.csv")
-
-clean_lamelo_data <-
-  raw_data_lamelo |>
-  select(Day, FieldGoalsMade, FieldGoalsAttempted,FieldGoalsPercentage, TwoPointersPercentage, ThreePointersPercentage, FreeThrowsPercentage, Minutes)|>
-  filter(Minutes > 0)
+# clean zion data and combine it #
+zion_2022 <- read_csv("data/raw_data/zion_data_2022.csv")
+zion_2023 <- read_csv("data/raw_data/zion_data_2023.csv")
 
 
-# clean maxey data
-raw_data_maxey <- read_csv("data/raw_data/raw_maxey_datasets.csv")
+# take out the month and wanted data, stack it together
+# merge two graphs by 2022 ontop of 2023, and then merge a table of the time to the left
 
-clean_maxey_data <-
-  raw_data_maxey |>
-  select(Day, FieldGoalsMade, FieldGoalsAttempted,FieldGoalsPercentage, TwoPointersPercentage, ThreePointersPercentage, FreeThrowsPercentage, Minutes)|>
-  filter(Minutes > 0)
+
+# clean maxey data and combine it #
+maxey_2022 <- read_csv("data/raw_data/maxey_data_2022.csv")
+maxey_2023 <- read_csv("data/raw_data/maxey_data_2023.csv")
+
+
+# clean lamelo data and combine it #
[…]

### 2024-04-22 scripts/00-simulate_data.R
removed incomplete player data and added complete player data

@@ -72,7 +72,7 @@ simulated_price_data <-
   tibble(
     # randomly select a year to assign to the ticket_count
     month_of_season = sample(
-      x = c("October", "November", "December", "January", "Feburary", "March", "April"),
+      x = c("October", "November", "December", "January", "February", "March", "April"),
       size = 1000,
       replace = TRUE
     ), 

### 2024-04-22 scripts/02-data_cleaning.R

@@ -17,6 +17,13 @@ library(arrow)
 #  janitor::clean_names()|>
 #  tidyr::drop_na()|>
 
+x <- c("2022-10-01", "2022-11-01", "2022-12-01", "2023-01-01", "2023-02-01", "2023-03-01", 
+       "2023-04-01", "2023-10-01", "2023-11-01", "2023-12-01", "2024-01-01", "2024-02-01", "2024-03-01", "2024-04-01")
+
+as.Date(x)
+
+# create the colum of dates that will get added to the left later.
+
 # clean zion data and combine it #
 zion_2022 <- read_csv("data/raw_data/zion_data_2022.csv")
 zion_2023 <- read_csv("data/raw_data/zion_data_2023.csv")

### 2024-04-23 paper/paper.qmd
fixed month data

@@
 
+The analysis of these three datasets will be carried out using the statistical programming language `R` [@citeR], using the `tidyverse`[@citetidy], `here`[@citehere], and `readxl`[@citexl] packages.
+The figures and tables in the paper are generated using the, respectively, `ggplot2`[@citegg] and `knitr`[@citeknitr] packages.
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+library(tidyverse)
+library(palmerpenguins)
+
+```
+
 # Model

### 2024-04-23 scripts/02-data_cleaning.R

@@ -11,47 +11,189 @@ library(tidyverse)
 library(janitor)
 library(tidyr)
 library(arrow)
-
+library(tibble)
 #### Clean data ####
 
 #  janitor::clean_names()|>
 #  tidyr::drop_na()|>
 
-x <- c("2022-10-01", "2022-11-01", "2022-12-01", "2023-01-01", "2023-02-01", "2023-03-01", 
+Months <- c("2022-10-01", "2022-11-01", "2022-12-01", "2023-01-01", "2023-02-01", "2023-03-01", 
        "2023-04-01", "2023-10-01", "2023-11-01", "2023-12-01", "2024-01-01", "2024-02-01", "2024-03-01", "2024-04-01")
 
-as.Date(x)
+format(as.Date(x), "%Y-%m")
 
 # create the colum of dates that will get added to the left later.
 
 # clean zion data and combine it #
-zion_2022 <- read_csv("data/raw_data/zion_data_2022.csv")
-zion_2023 <- read_csv("data/raw_data/zion_data_2023.csv")
-
-
-# take out the month and wanted data, stack it together
-# merge two graphs by 2022 ontop of 2023, and then merge a table of the time to the left
+clean_price_data <- read_csv("data/raw_data/card_price.csv")
 
 
 # clean maxey data and combine it #
 maxey_2022 <- read_csv("data/raw_data/maxey_data_2022.csv")
 maxey_2023 <- read_csv("data/raw_data/maxey_data_2023.csv")
 
+temp_maxey_2022 <-
+maxey_2022 |>
+  filter(
+           X1...1 == "October"| 
+           X1...1 == "November"| 
+           X1...1 == "December"| 
+           X1...1 == "January"|
+           X1...1 == "February"|
+           X1...1 == "March"|
+           X1...1 == "April") |>
+  select(X11, X12, X13, X14, X17)
+
+
+temp_maxey_2023 <-
+maxey_2023 |>
+  filter(X1...1 == "October"| 
+           X1...1 == "November"| 
+           X1...1 == "December"| 
+           X1...1 == "January"|
+           X1...1 == "February"|
+           X1...1 == "March"|
+           X1...1 == "April") |>
+  select(X11, X12, X13, X14, X17)
+  
+
+clean_maxey <- rbind(temp_maxey_2022, temp_maxey_2023)|>
+  rename(
+    REB = X11,
+    AST = X12,
[…]

### 2024-04-23 scripts/03-test_data.R

@@ -18,51 +18,202 @@ library(janitor)
 
 # read cleaned player data
 
-test_zion_data = read_csv(
-  file = "data/analysis_data/cleaned_zion_data.csv",
-  show_col_types = FALSE
-)
 
-test_lamelo_data = read_csv(
-  file = "data/analysis_data/cleaned_maxey_data.csv",
+test_anthony_edward = read_csv(
+  file = "data/analysis_data/clean_anthony_edward.csv",
   show_col_types = FALSE
 )
 
 test_haliburton_data = read_csv(
-  file = "data/analysis_data/cleaned_lamelo_data.csv",
+  file = "data/analysis_data/clean_haliburton.csv",
   show_col_types = FALSE
 )
 
 test_maxey_data = read_csv(
-  file = "data/analysis_data/cleaned_haliburton_data.csv",
+  file = "data/analysis_data/clean_maxey.csv",
   show_col_types = FALSE
 )
 
+test_price = read_csv(
+  file = "data/analysis_data/clean_price_data.csv",
+  show_col_types = FALSE
+)
 
+### Test anthony_edward data above ###
 
-### Test the data above ###
-
-# Test zion data #
-if (min(test_zion_data$Minutes) < 1) {
-  print("Game when player did not play detected")
+# Test for negativescore 
+if (min(test_anthony_edward$PTS) < 0) {
+  print("Month with negative score detected")
 }
 
-if (max(test_zion_data$Minutes) > 48) {
+# testing for realistic point average for the month
+if (max(test_anthony_edward$PTS) > 50) {
   print("Player played more than max possible time")
 }
 
-if (min(test_youth_data$ticket_count) < 0) {
-  print("Negative number in ticket count")
+# testing if blocks average was below 0
+if (min(test_anthony_edward$BLK) < 0) {
+  print("Month with negative score detected")
 }
 
-if (min(test_youth_data$ticket_count) < 0) {
-  print("Negative number in ticket count")
+# testing for realistic blocks average for the month
+if (max(test_anthony_edward$BLK) > 20) {
+  print("Player blocks average may be unrealistic")
 }
 
-if (min(test_youth_data$ticket_count) < 0) {
-  print("Negative number in ticket count")
+# testing if steal average was below 0
+if (min(test_anthony_edward$STL) < 0) {
+  print("Month with negative score detected")
 }
 
-# Test lamelo data #
+# testing for realistic steal average for the month
[…]

### 2024-04-23 paper/paper.qmd
added introduction, player data table

@@
 ---
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+library(tidyverse)
+library(arrow)
+library(here)
+library(palmerpenguins)
+library(knitr)
+library(rstanarm)
+
+# load data
+anthony_edward = read_csv(
+  file = "/Users/harrison/NBA/data/analysis_data/clean_anthony_edward.csv",
+  show_col_types = FALSE
+)
+
+haliburton = read_csv(
+  file = "/Users/harrison/NBA/data/analysis_data/clean_haliburton.csv",
+  show_col_types = FALSE
+)
+
+maxey = read_csv(
+  file = "/Users/harrison/NBA/data/analysis_data/clean_maxey.csv",
+  show_col_types = FALSE
+)
+
+price_data = read_csv(
+  file = "/Users/harrison/NBA/data/analysis_data/clean_price_data.csv",
+  show_col_types = FALSE
+)
+```
 
@@
 
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-
-library(tidyverse)
-library(palmerpenguins)
-```
-
 # Data
 
-Talk more about it. Data used here are unmanipulated data, simply created by graph functions with the data sets.
+Data used here are unmanipulated data, simply created by graph functions with the data sets.
+
+The first place the data was collected from is ESPN API, player statistics were obtained from scrapping the website and picking out the right tables.
+Please be respectful if you decide to use it for any other purpose.
+Each player had multiple tables and I downloaded the tables and merged players’ 202202-2023 and 2023-2024 data.
+This allows all statistics to be viewed in one table.
+In addition, when considering which of the statistics to focus on, I asked an NBA reporter Lisa Kao for suggestions.
+She mentioned that average points, blocks, steals, and assists are the top 5 statistics focused on in the industry.
+
+The second source of the data came from Sportscardpro website.
+They collect data from eBay's successful transactions of the card and gather them onto their website.
+Since there was no table to download the data, I had to manually create an Excel file with the data presented on the website and then import it into rStudio.
+The price focuses on the PSA 10 and Prizm Silver series of that specific player's rookie card.
 
@@
 The figures and tables in the paper are generated using the, respectively, `ggplot2`[@citegg] and `knitr`[@citeknitr] packages.
+
+## Player Statistics
+
+Below is a brief explination of the tables including player statistics:
+
+1. The `REB` column refers to the number of rebounds the player average per game in that month.
+2. The `AST` column refers to the number of assists the player average per game in that month.
+3. The `BLK` column refers to the number of blocks the player average per game in that month.
+4. The `STL` column refers to the number of steals the player average per game in that month.
+5. The `PTS` column refers to the number of points the player average per game in that month.
+
 ```{r}
-#| include: false
+#| label: tbl-1
+#| tbl-cap: The data set containing player statistics of Anthon Edward from 2022 to 2024
+#| echo: false
 #| warning: false
-#| message: false
 
-library(tidyverse)
-library(palmerpenguins)
+head(anthony_edward, padding = 5)
+```
 
+```{r}
+#| label: tbl-2
+#| tbl-cap: The data set containing player statistics of Tyrese Maxey from 2022 to 2024
+#| echo: false
+#| warning: false
+
+head(anthony_edward, padding = 5)
 ```
+
+```{r}
+#| label: tbl-3
+#| tbl-cap: The data set containing player statistics of Tyrese Haliburton from 2022 to 2024
+#| echo: false
+#| warning: false
+
+head(anthony_edward, padding = 5)
+```
+
+ @tbl-1, @tbl-2, and  @tbl-3 are the three player statistics data that will be used in the model.
+
+## Card Price statistics
 

### 2024-04-23 scripts/02-data_cleaning.R

@@ -20,12 +20,24 @@ library(tibble)
 Months <- c("2022-10-01", "2022-11-01", "2022-12-01", "2023-01-01", "2023-02-01", "2023-03-01", 
        "2023-04-01", "2023-10-01", "2023-11-01", "2023-12-01", "2024-01-01", "2024-02-01", "2024-03-01", "2024-04-01")
 
-format(as.Date(x), "%Y-%m")
+Months <- format(as.Date(Months), "%Y-%m")
+
 
 # create the colum of dates that will get added to the left later.
 
-# clean zion data and combine it #
+
 clean_price_data <- read_csv("data/raw_data/card_price.csv")
+
+view(clean_price_data)
+
+clean_price_data <- clean_price_data[-c(8), ]
+clean_price_data$`2022-23` <- NULL
+
+clean_price_data <-
+  clean_price_data|>
+  add_column(Date = Months, .before = "LaMelo")
+
+view(clean_price_data)
 
 
 # clean maxey data and combine it #
@@ -66,9 +78,9 @@ clean_maxey <- rbind(temp_maxey_2022, temp_maxey_2023)|>
     PTS = X17
   )
 
-add_column(clean_maxey, Months, .before = "REB")
+clean_maxey <- add_column(clean_maxey, Months, .before = "REB")
   
-
+view(clean_maxey)
 
 # clean lamelo data and combine it #
 lamelo_2022 <- read_csv("data/raw_data/lamelo_data_2022.csv")
@@ -111,7 +123,7 @@ clean_lamelo <- rbind(temp_lamelo_2022, temp_lamelo_2023)|>
   )
 
 view(clean_lamelo)
-add_column(clean_lamelo, Months, .before = "REB")
+clean_lamelo <- add_column(clean_lamelo, Months, .before = "REB")
 
 
 # clean haliburton data and combine it #
@@ -153,7 +165,8 @@ clean_haliburton <- rbind(temp_haliburton_2022, temp_haliburton_2023)|>
   )
 
 
-add_column(clean_haliburton, Months, .before = "REB")
+clean_haliburton <- add_column(clean_haliburton, Months, .before = "REB")
+
 
 # clean anthony_edward data and combine it #
 anthony_edward_2022 <- read_csv("data/raw_data/anthony_edward_data_2022.csv")
@@ -193,15 +206,16 @@ clean_anthony_edward <- rbind(temp_anthony_edward_2022, temp_anthony_edward_2023
[…]

### 2024-04-23 paper/paper.qmd
added tables

@@
 
+```{r}
+#| label: tbl-4
+#| tbl-cap: This table is the Prizm Silver RC card price monthly from 2022 season to the end of 2023 season. 
+#| echo: false
+#| warning: false
+
+head(price_data, padding = 5)
+```
+
+The table above @tbl-4 includes card price.
+The player card price is from a website called Sportscardpro, they collect data from eBay's successful transactions of the card and gather them onto their website.
+Since there was no table to download the data, I had to manually create an Excel file with the data presented on the website and then import it into rStudio.
+The price focuses on the PSA 10 and Prizm Silver series of that specific player's rookie card.
+
 # Model
 
-The goal of our modelling strategy is twofold. Firstly,...
+The goal of this paper's modelling strategy is to investigate the effect that average player statistics has on their price of the PSA 10 Prizm Silver rookie card.
+Since we expect the relationship to be positively related, if a player plays better, the price of their Rookie Card should increase, therefore we will use a linear regression model.
+I will use the model to make potential prediction of the upcoming price of the player card based on their current statistics and price data.
 
@@
 
+## Average player statistics
+
+## Price trend ratio to player average
+
 # Discussion
@@
 
-Weaknesses and next steps should also be included.
+Weaknesses and next steps should also be included. More player should be added into this analysis and
 

### 2024-04-23 scripts/03-test_data.R

@@ -18,7 +18,6 @@ library(janitor)
 
 # read cleaned player data
 
-
 test_anthony_edward = read_csv(
   file = "data/analysis_data/clean_anthony_edward.csv",
   show_col_types = FALSE

### 2024-04-24 paper/paper.qmd
added models

@@
 
+## Model preduction
+
+```{r}
+#| echo: false
+#| warning: false
+
+test_maxey <- tibble(
+  REB = c(
+    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
+  ),
+  AST = c(
+    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
+  ),
+  BLK = c(
+    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
+  ),
+  STL = c(
+    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
+  ),
+  PTS = c(
+    20, 25, 40, 30, 45, 20, 30, 35, 20, 15, 35, 30, 35, 20 
+  )
+)
+
+view(test_maxey)
+
+maxey_prediction <- predict(maxey_model, newdata = test_maxey)
+
+```
+
+```{r}
+#| label: tbl-5
+#| tbl-cap: This table is the prediction price of Tyrese Maxey RC Prizm Silver card using the model 
+#| echo: false
+#| warning: false
+
+kable(maxey_prediction, padding = 5)
+
+view(maxey_prediction)
+```
+
 ### Model justification
@@
 
+## Model Check
+
+```{r}
+library(rstanarm)
+
+pp_check(maxey_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(maxey_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+```
+
 \newpage

### 2024-04-24 scripts/04-model.R

@@ -1,37 +1,105 @@
 #### Preamble ####
 # Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Harrison Huang
+# Date: April 23, 2024
+# Contact: Harri.huang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: N/A
+# Any other information needed? N/A
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+price_data <- read_csv("data/analysis_data/clean_price_data.csv")
+
+maxey <- read_csv("data/analysis_data/clean_maxey.csv")
+haliburton <- read_csv("data/analysis_data/clean_haliburton.csv")
+anthony <- read_csv("data/analysis_data/clean_anthony_edward.csv")
+
+## creating data set for tyrese maxey
+temp_maxey_price <-
+  price_data|>
+  select(`Tyrese Maxey`)
+
+maxey_and_price <- add_column(maxey, temp_maxey_price)
+
+
+## creating data set for tyrese haliburton
+temp_haliburton_price <-
+  price_data|>
+  select(`Tyrese Haliburton`)
+
+haliburton_and_price <- add_column(haliburton, temp_haliburton_price)
+
+
+# creating data set for anthony edward
+temp_anthony_price <-
+  price_data|>
+  select(`Anthony Edward`)
+
+anthony_and_price <- add_column(anthony, temp_anthony_price)
+
 
 ### Model data ####
-first_model <-
+
+## Maxey Model ##
+maxey_model <-
   stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
+    formula = `Tyrese Maxey` ~ REB + AST + STL + BLK + PTS,
+    data = maxey_and_price,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
[…]

### 2024-04-24 paper/paper.qmd
fixed model and added writing

@@
 This analysis will use player statistics to create a model to try to grasp possible future price trends of the card.
-A xxx model was used in this analysis.
-The results indicated that xxx is a strong indicator of the price fluctuation of potential future prices of the rookie card."
+A linear model was used in this analysis.
+The results indicated that player statistics may still not be sufficient to predict future prices of the rookie card."
 format: pdf
@@
 ---
+```{r}
+#library(readr)
+#write_bib()
+```
 
@@
 )
+
+maxey_model <- read_rds("/Users/harrison/NBA/models/maxey_model.rds")
+haliburton_model <- read_rds("/Users/harrison/NBA/models/haliburton_model.rds")
+anthony_model <- read_rds("/Users/harrison/NBA/models/anthony_model.rds")
+
 ```
@@
 
-This analysis finds that….
+This analysis finds that there are a lot more than performance linking to the price of the rookie card.
+The performance statistics is only a some of the reasons fluctuating card prices.
+There are so much more than just the performance of the rookie when taking in consideration of price analysis.
+Future steps will needed in order to take a look at more factors that may affect the price of the rookie card of that specific player.
 
-	In Section 2 of the paper, the source and datasets are discussed.
+	In Section 2 of the paper, the source and data sets are discussed.
 Strengths and weaknesses, methods of collection, and terminologies will be explored.
@@
 
-Data used here are unmanipulated data, simply created by graph functions with the data sets.
-
-The first place the data was collected from is ESPN API, player statistics were obtained from scrapping the website and picking out the right tables.
+The first place the data was collected from is ESPN, player statistics were obtained from scrapping the website and picking out the right tables.
 Please be respectful if you decide to use it for any other purpose.
@@
 She mentioned that average points, blocks, steals, and assists are the top 5 statistics focused on in the industry.
+Something to keep in mind is that these statistics presented are all positive statistics, which means that the higher the number the better the player has performed.
 
@@
 
- @tbl-1, @tbl-2, and  @tbl-3 are the three player statistics data that will be used in the model.
+In @tbl-1, @tbl-2, and  @tbl-3 are the three player statistics data that will be used in the model.
 
@@
 
-The table above @tbl-4 includes card price.
+The table above @tbl-4 includes the card price.
 The player card price is from a website called Sportscardpro, they collect data from eBay's successful transactions of the card and gather them onto their website.
@@
 The price focuses on the PSA 10 and Prizm Silver series of that specific player's rookie card.
+Initially, I was going to include data for Zion and LaMelo, however, due to injuries that occurred throughout their career, the player statistics were inconsistent and had a lot of missing months.
+For those reasons, I will only be following forward with Tyrese Maxey, Tyrese Haliburton, and Anthony Edward.
 
@@
 The goal of this paper's modelling strategy is to investigate the effect that average player statistics has on their price of the PSA 10 Prizm Silver rookie card.
-Since we expect the relationship to be positively related, if a player plays better, the price of their Rookie Card should increase, therefore we will use a linear regression model.
-I will use the model to make potential prediction of the upcoming price of the player card based on their current statistics and price data.
+I will then use the model to make potential prediction of the upcoming price of the player card based on their current statistics and price data.
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define $y_i$ as the price of the PSA10 Prizm Silver rookie card.
+Then $\beta_1$ is the average rebounds a player gets per game, $\gamma_1$ is the average assists a player gets per game, $\theta_1$ is the average blocks a player gets per game, $\phi_1$ is the average steals a player gets per game, and lastly, $\kappa_1$ is the average points a player gets per game.
+This is the same for all the player, since each players' statistics and card price likely independent, I will use the same model on the three players, Tyrese Haliburton, Tyrese Maxey, and Anthony Edward.
 
@@
 y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
+\mu_i &= \alpha + \theta_i + \phi_i + \kappa_i + \beta_i * \gamma_i \\
 \alpha &\sim \mbox{Normal}(0, 2.5) \\
@@
 \gamma &\sim \mbox{Normal}(0, 2.5) \\
+\theta &\sim \mbox{Normal}(0, 2.5) \\
+\phi &\sim \mbox{Normal}(0, 2.5) \\
+\kappa &\sim \mbox{Normal}(0, 2.5) \\
 \sigma &\sim \mbox{Exponential}(1)
@@
 
-## Model preduction
+### Model justification
+
+We expect a positive relationship between the statistics of the player and price of their rookie trading card.
+Usually, if a player plays better, the price of their Rookie Card should increase, therefore we will use a linear regression model.
+
+## Model prediction
+
+I will create a test data set for 2024-2025 and 2026-2027 season and use the model with this test data set to predict the price of these players using their own model.
+In @tbl-5, @tbl-6, and @tbl-7 are the predicted data based by improving the players statistics slightly.
+
+### Tyrese Maxey prediction
 
@@
 #| warning: false
+
+Months <- c("2024-10-01", "2024-11-01", "2024-12-01", "2025-01-01", "2025-02-01", "2025-03-01", 
+       "2025-04-01", "2026-10-01", "2026-11-01", "2026-12-01", "2027-01-01", "2027-02-01", "2027-03-01", "2027-04-01")
+
+Months_data <- format(as.Date(Months), "%Y-%m")
 
@@
 
-view(test_maxey)
-
 maxey_prediction <- predict(maxey_model, newdata = test_maxey)
 
+# code found to turn table from veticle to horizontal: https://youtu.be/dE6Z3mJdero
+
+maxey_prediction_table <- data.frame(maxey_prediction)
+maxey_prediction_table <- add_column(maxey_prediction_table, Months_data)
+
+colnames(maxey_prediction_table) <- c("Predicted Price", "Month")
 ```
@@
 
-kable(maxey_prediction, padding = 5)
+kable(maxey_prediction_table, padding = 5)
 
-view(maxey_prediction)
 ```
 
-### Model justification
+### Tyrese Haliburton prediction
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+```{r}
+#| echo: false
+#| warning: false
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+test_haliburton <- tibble(
+  REB = c(
+    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
+  ),
+  AST = c(
+    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
+  ),
+  BLK = c(
+    4.5, 4.3, 5.1, 3.1, 4.5, 2.6, 3.8, 4.5, 2.5, 4.1, 4.3, 4.5, 5.8, 5.5
+  ),
+  STL = c(
+    4.5, 4.3, 2.1, 3.1, 4.5, 2.6, 4.8, 4.5, 6.5, 4.1, 4.3, 4.5, 2.8, 4.5
+  ),
+  PTS = c(
+    20, 25, 10, 30, 25, 20, 30, 35, 20, 15, 35, 30, 35, 20 
+  )
+)
+
+haliburton_prediction <- predict(haliburton_model, newdata = test_haliburton)
+
+# code found to turn table from vertical to horizontal: https://youtu.be/dE6Z3mJdero
+
+haliburton_prediction_table <- data.frame(haliburton_prediction)
+haliburton_prediction_table <- add_column(haliburton_prediction_table, Months_data)
+
+colnames(haliburton_prediction_table) <- c("Predicted Price", "Month")
+
+view(haliburton_prediction_table)
+```
+
+```{r}
+#| label: tbl-6
+#| tbl-cap: This table is the prediction price of Tyrese Haliburton RC Prizm Silver card using the model
+#| echo: false
+#| warning: false
+
+kable(haliburton_prediction_table, padding = 5)
+
+```
+
+### Anthony Edward prediction
+
+```{r}
+#| echo: false
+#| warning: false
+
+test_anthony <- tibble(
+  REB = c(
+    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
+  ),
+  AST = c(
+    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
+  ),
+  BLK = c(
+    4.5, 4.3, 5.1, 3.1, 4.5, 2.6, 3.8, 4.5, 2.5, 4.1, 4.3, 4.5, 5.8, 5.5
+  ),
+  STL = c(
+    4.5, 4.3, 2.1, 3.1, 4.5, 2.6, 4.8, 4.5, 6.5, 4.1, 4.3, 4.5, 2.8, 4.5
+  ),
+  PTS = c(
+    20, 25, 10, 30, 25, 20, 30, 35, 20, 15, 35, 30, 35, 20 
+  )
+)
+
+anthony_prediction <- predict(anthony_model, newdata = test_anthony)
+
+# code found to turn table from vertical to horizontal: https://youtu.be/dE6Z3mJdero
+
+anthony_prediction_table <- data.frame(anthony_prediction)
+anthony_prediction_table <- add_column(anthony_prediction_table, Months_data)
+
+colnames(anthony_prediction_table) <- c("Predicted Price", "Month")
+
+view(anthony_prediction_table)
+```
+
+```{r}
+#| label: tbl-7
+#| tbl-cap: This table is the prediction price of Anthony Edward RC Prizm Silver card using the model
+#| echo: false
+#| warning: false
+
+kable(anthony_prediction_table, padding = 5)
+
+```
 
@@
 
-## First discussion point {#sec-first-point}
+## First discussion point
 
@@
 
-pp_check(maxey_model) +
+pp_check(haliburton_model) +
   theme_classic() +
@@
 
-posterior_vs_prior(maxey_model) +
+posterior_vs_prior(haliburton_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+
+pp_check(anthony_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(anthony_model) +
   theme_minimal() +

### 2024-04-24 scripts/04-model.R

@@ -35,6 +35,7 @@ temp_haliburton_price <-
 
 haliburton_and_price <- add_column(haliburton, temp_haliburton_price)
 
+view(haliburton_and_price)
 
 # creating data set for anthony edward
 temp_anthony_price <-
@@ -43,7 +44,7 @@ temp_anthony_price <-
 
 anthony_and_price <- add_column(anthony, temp_anthony_price)
 
-
+view(anthony_and_price)
 ### Model data ####
 
 ## Maxey Model ##
@@ -81,8 +82,6 @@ anthony_model <-
     prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 888
   )
-
-
 
 
 

### 2024-04-24 paper/paper.qmd
saved paper
fixed rendering issue

@@
 ```{r}
-#library(readr)
-#write_bib()
-```
-
-```{r}
 #| include: false
@@
 library(rstanarm)
+
+library(readr)
+#write_bib()
 
@@
   file = "/Users/harrison/NBA/data/analysis_data/clean_price_data.csv",
+  show_col_types = FALSE
+)
+
+maxey_and_price = read_csv(
+  file = "/Users/harrison/NBA/data/analysis_data/maxey_and_price.csv",
+  show_col_types = FALSE
+)
+
+haliburton_and_price = read_csv(
+  file = "/Users/harrison/NBA/data/analysis_data/haliburton_and_price.csv",
+  show_col_types = FALSE
+)
+
+anthony_and_price = read_csv(
+  file = "/Users/harrison/NBA/data/analysis_data/anthony_and_price.csv",
   show_col_types = FALSE
@@
 
-head(anthony_edward, padding = 5)
+kable(anthony_edward, padding = 5)
 ```
@@
 
-head(anthony_edward, padding = 5)
+kable(maxey, padding = 5)
 ```
@@
 
-head(anthony_edward, padding = 5)
+kable(haliburton, padding = 5)
 ```
@@
 
-head(price_data, padding = 5)
+kable(price_data, padding = 5)
 ```
@@
 
-view(haliburton_prediction_table)
 ```
@@
 kable(haliburton_prediction_table, padding = 5)
-
 ```
@@
 ```{r}
-library(rstanarm)
+#| include: true
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+
+pp_check(maxey_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(maxey_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
 

### 2024-04-24 scripts/02-data_cleaning.R

@@ -208,17 +208,44 @@ clean_anthony_edward <- rbind(temp_anthony_edward_2022, temp_anthony_edward_2023
 
 clean_anthony_edward <- add_column(clean_anthony_edward, Months, .before = "REB")
 
-view(clean_anthony_edward)
+
+## Create data for model ##
+
+## creating data set for tyrese maxey
+temp_maxey_price <-
+  price_data|>
+  select(`Tyrese Maxey`)
+
+maxey_and_price <- add_column(clean_maxey, temp_maxey_price)
+
+
+## creating data set for tyrese haliburton
+temp_haliburton_price <-
+  price_data|>
+  select(`Tyrese Haliburton`)
+
+haliburton_and_price <- add_column(clean_haliburton, temp_haliburton_price)
+
+
+# creating data set for anthony edward
+temp_anthony_price <-
+  price_data|>
+  select(`Anthony Edward`)
+
+anthony_and_price <- add_column(clean_anthony_edward, temp_anthony_price)
+
 #### Save data ####
 
 # becase of errors that occur throughout the attemts to save files as  parquet, the files will not be saved as parquet format. 
 #Error in parquet___WriterProperties___Builder__create() : 
 #Cannot call parquet___WriterProperties___Builder__create(). See https://arrow.apache.org/docs/r/articles/install.html for help installing Arrow C++ libraries. 
 
-view(clean_maxey)
 write_csv(clean_maxey, "data/analysis_data/clean_maxey.csv")
 write_csv(clean_haliburton, "data/analysis_data/clean_haliburton.csv")
 write_csv(clean_anthony_edward, "data/analysis_data/clean_anthony_edward.csv")
 write_csv(clean_price_data, "data/analysis_data/clean_price_data.csv")
 
+write_csv(maxey_and_price, "data/analysis_data/maxey_and_price.csv")
+write_csv(haliburton_and_price, "data/analysis_data/haliburton_and_price.csv")
+write_csv(anthony_and_price, "data/analysis_data/anthony_and_price.csv")
 

### 2024-04-24 scripts/04-model.R

@@ -14,37 +14,12 @@ library(rstanarm)
 library(arrow)
 
 #### Read data ####
-price_data <- read_csv("data/analysis_data/clean_price_data.csv")
 
-maxey <- read_csv("data/analysis_data/clean_maxey.csv")
-haliburton <- read_csv("data/analysis_data/clean_haliburton.csv")
-anthony <- read_csv("data/analysis_data/clean_anthony_edward.csv")
-
-## creating data set for tyrese maxey
-temp_maxey_price <-
-  price_data|>
-  select(`Tyrese Maxey`)
-
-maxey_and_price <- add_column(maxey, temp_maxey_price)
+maxey_and_price <- read_csv("data/analysis_data/maxey_and_price.csv")
+haliburton_and_price <- read_csv("data/analysis_data/haliburton_and_price.csv")
+anthony_and_price <- read_csv("data/analysis_data/anthony_and_price.csv")
 
 
-## creating data set for tyrese haliburton
-temp_haliburton_price <-
-  price_data|>
-  select(`Tyrese Haliburton`)
-
-haliburton_and_price <- add_column(haliburton, temp_haliburton_price)
-
-view(haliburton_and_price)
-
-# creating data set for anthony edward
-temp_anthony_price <-
-  price_data|>
-  select(`Anthony Edward`)
-
-anthony_and_price <- add_column(anthony, temp_anthony_price)
-
-view(anthony_and_price)
 ### Model data ####
 
 ## Maxey Model ##
@@ -101,4 +76,5 @@ saveRDS(
   anthony_model,
   file = "models/anthony_model.rds"
 )
+
 

### 2024-04-24 paper/paper.qmd
updated mock data for model

@@
 In @tbl-5, @tbl-6, and @tbl-7 are the predicted data based by improving the players statistics slightly.
+The mock data wick use the original data from 2022 to 2024 with an increase of 2% each month to see if increasing performance statistics have an impact on the card price.
 
@@
 
-test_maxey <- tibble(
-  REB = c(
-    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
-  ),
-  AST = c(
-    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
-  ),
-  BLK = c(
-    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
-  ),
-  STL = c(
-    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
-  ),
-  PTS = c(
-    20, 25, 40, 30, 45, 20, 30, 35, 20, 15, 35, 30, 35, 20 
-  )
-)
+test_maxey_price_only <- clean_maxey[, -1]
 
-maxey_prediction <- predict(maxey_model, newdata = test_maxey)
+test_maxey_price_only[1, ] <- (test_maxey_price_only[1, ])*1.02
+test_maxey_price_only[2, ] <- (test_maxey_price_only[2, ])*1.04
+test_maxey_price_only[3, ] <- (test_maxey_price_only[3, ])*1.06
+test_maxey_price_only[4, ] <- (test_maxey_price_only[4, ])*1.08
+test_maxey_price_only[5, ] <- (test_maxey_price_only[5, ])*1.10
+test_maxey_price_only[6, ] <- (test_maxey_price_only[6, ])*1.12
+test_maxey_price_only[7, ] <- (test_maxey_price_only[7, ])*1.14
+test_maxey_price_only[8, ] <- (test_maxey_price_only[8, ])*1.16
+test_maxey_price_only[9, ] <- (test_maxey_price_only[9, ])*1.18
+test_maxey_price_only[10, ] <- (test_maxey_price_only[10, ])*1.20
+test_maxey_price_only[11, ] <- (test_maxey_price_only[1, ])*1.22
+test_maxey_price_only[12, ] <- (test_maxey_price_only[12, ])*1.24
+test_maxey_price_only[13, ] <- (test_maxey_price_only[13, ])*1.26
+test_maxey_price_only[14, ] <- (test_maxey_price_only[14, ])*1.28
+
+maxey_prediction <- predict(maxey_model, newdata = test_maxey_price_only)
 
@@
 
-test_haliburton <- tibble(
-  REB = c(
-    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
-  ),
-  AST = c(
-    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
-  ),
-  BLK = c(
-    4.5, 4.3, 5.1, 3.1, 4.5, 2.6, 3.8, 4.5, 2.5, 4.1, 4.3, 4.5, 5.8, 5.5
-  ),
-  STL = c(
-    4.5, 4.3, 2.1, 3.1, 4.5, 2.6, 4.8, 4.5, 6.5, 4.1, 4.3, 4.5, 2.8, 4.5
-  ),
-  PTS = c(
-    20, 25, 10, 30, 25, 20, 30, 35, 20, 15, 35, 30, 35, 20 
-  )
-)
+test_haliburton_price_only <- clean_haliburton[, -1]
 
-haliburton_prediction <- predict(haliburton_model, newdata = test_haliburton)
+test_haliburton_price_only[1, ] <- (test_haliburton_price_only[1, ])*1.02
+test_haliburton_price_only[2, ] <- (test_haliburton_price_only[2, ])*1.04
+test_haliburton_price_only[3, ] <- (test_haliburton_price_only[3, ])*1.06
+test_haliburton_price_only[4, ] <- (test_haliburton_price_only[4, ])*1.08
+test_haliburton_price_only[5, ] <- (test_haliburton_price_only[5, ])*1.10
+test_haliburton_price_only[6, ] <- (test_haliburton_price_only[6, ])*1.12
+test_haliburton_price_only[7, ] <- (test_haliburton_price_only[7, ])*1.14
+test_haliburton_price_only[8, ] <- (test_haliburton_price_only[8, ])*1.16
+test_haliburton_price_only[9, ] <- (test_haliburton_price_only[9, ])*1.18
+test_haliburton_price_only[10, ] <- (test_haliburton_price_only[10, ])*1.20
+test_haliburton_price_only[11, ] <- (test_haliburton_price_only[1, ])*1.22
+test_haliburton_price_only[12, ] <- (test_haliburton_price_only[12, ])*1.24
+test_haliburton_price_only[13, ] <- (test_haliburton_price_only[13, ])*1.26
+test_haliburton_price_only[14, ] <- (test_haliburton_price_only[14, ])*1.28
+
+haliburton_prediction <- predict(haliburton_model, newdata = test_haliburton_price_only)
 
@@
 
-test_anthony <- tibble(
-  REB = c(
-    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
-  ),
-  AST = c(
-    4.5, 4.3, 5.1, 3.1, 4.5, 5.6, 7.8, 4.5, 6.5, 4.1, 4.3, 6.5, 5.8, 5.5
-  ),
-  BLK = c(
-    4.5, 4.3, 5.1, 3.1, 4.5, 2.6, 3.8, 4.5, 2.5, 4.1, 4.3, 4.5, 5.8, 5.5
-  ),
-  STL = c(
-    4.5, 4.3, 2.1, 3.1, 4.5, 2.6, 4.8, 4.5, 6.5, 4.1, 4.3, 4.5, 2.8, 4.5
-  ),
-  PTS = c(
-    20, 25, 10, 30, 25, 20, 30, 35, 20, 15, 35, 30, 35, 20 
-  )
-)
+test_anthony_price_only <- clean_anthony_edward[, -1]
 
-anthony_prediction <- predict(anthony_model, newdata = test_anthony)
+test_anthony_price_only[1, ] <- (test_anthony_price_only[1, ])*1.02
+test_anthony_price_only[2, ] <- (test_anthony_price_only[2, ])*1.04
+test_anthony_price_only[3, ] <- (test_anthony_price_only[3, ])*1.06
+test_anthony_price_only[4, ] <- (test_anthony_price_only[4, ])*1.08
+test_anthony_price_only[5, ] <- (test_anthony_price_only[5, ])*1.10
+test_anthony_price_only[6, ] <- (test_anthony_price_only[6, ])*1.12
+test_anthony_price_only[7, ] <- (test_anthony_price_only[7, ])*1.14
+test_anthony_price_only[8, ] <- (test_anthony_price_only[8, ])*1.16
+test_anthony_price_only[9, ] <- (test_anthony_price_only[9, ])*1.18
+test_anthony_price_only[10, ] <- (test_anthony_price_only[10, ])*1.20
+test_anthony_price_only[11, ] <- (test_anthony_price_only[1, ])*1.22
+test_anthony_price_only[12, ] <- (test_anthony_price_only[12, ])*1.24
+test_anthony_price_only[13, ] <- (test_anthony_price_only[13, ])*1.26
+test_anthony_price_only[14, ] <- (test_anthony_price_only[14, ])*1.28
+
+anthony_prediction <- predict(anthony_model, newdata = test_anthony_price_only)
 
@@
 
-view(anthony_prediction_table)
 ```
@@
 
-## Average player statistics
+## Price of increasing performance
 

### 2024-04-24 scripts/02-data_cleaning.R

@@ -78,9 +78,19 @@ clean_maxey <- rbind(temp_maxey_2022, temp_maxey_2023)|>
     PTS = X17
   )
 
+clean_maxey <-
+  clean_maxey |>
+  mutate(
+    REB = as.double(REB),
+    AST = as.double(AST),
+    BLK = as.double(BLK),
+    STL = as.double(STL),
+    PTS = as.double(PTS),
+  )
+
+
 clean_maxey <- add_column(clean_maxey, Months, .before = "REB")
   
-view(clean_maxey)
 
 # clean lamelo data and combine it #
 lamelo_2022 <- read_csv("data/raw_data/lamelo_data_2022.csv")
@@ -164,6 +174,15 @@ clean_haliburton <- rbind(temp_haliburton_2022, temp_haliburton_2023)|>
     PTS = X17
   )
 
+clean_haliburton <-
+  clean_haliburton |>
+    mutate(
+      REB = as.double(REB),
+      AST = as.double(AST),
+      BLK = as.double(BLK),
+      STL = as.double(STL),
+      PTS = as.double(PTS),
+    )
 
 clean_haliburton <- add_column(clean_haliburton, Months, .before = "REB")
 
@@ -205,6 +224,17 @@ clean_anthony_edward <- rbind(temp_anthony_edward_2022, temp_anthony_edward_2023
     STL = X14,
     PTS = X17
   )
+
+clean_anthony_edward <-
+  clean_anthony_edward |>
+  mutate(
+    REB = as.double(REB),
+    AST = as.double(AST),
+    BLK = as.double(BLK),
+    STL = as.double(STL),
+    PTS = as.double(PTS),
+  )
+
 
 clean_anthony_edward <- add_column(clean_anthony_edward, Months, .before = "REB")
 

### 2024-04-24 paper/paper.qmd
added discussion

@@
 
-## Price trend ratio to player average
-
 # Discussion
 
-## First discussion point
+## Overall price trend
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+The player's performance does not have too much of a prediction factor in the price of their card.
+Overall, almost every player has a downward trend in price regardless of how they are performing in the league.
+I think this has to do with the initial overvaluation of the card.
+The quantity that is released into the market also plays a critical role in the price.
+As we know, the more supply, and if the demand can’t keep up with the supply, then the price will go down.
+With more packs of cards being opened every day, the number of cards being released into the market also increases.
 
-## Second discussion point
+## Confounding variables
+The linear model may be too simple due to each player's positions and playstyles.
+Because we are assuming that the higher the statistics are the better a player is performing.
+However, basketball is not only about statistics.
+If a player is known and in charge of defensive plays, their blocks and rebounds may be more important compared to attack-oriented players.
+The behavior of a player outside the league is also very crucial in terms of this.
+Even though Ja Morant played well in the league, he had multiple occasions where he displayed illegal objects during his livestream on Instagram.
+This devastated his reputation overall and he also received game restrictions as punishment.
+His card price also plummeted from around 2000 to now at around 400 dollars.
 
@@
 
-Weaknesses and next steps should also be included. More player should be added into this analysis and
+Since there isn’t a major platform that provides the tracking of every transaction of a card, it is very difficult to obtain the true price of the card.
+Sportscardpro only gathers its data from completed transactions of that card on eBay, which is only a portion of the sales that happen on the internet.
+Transactions of the card that often happen offline in stores are also not tracked, if I sold a card to my friend for a cheaper price, it is not reflected in the dataset from Sportscardpro.
+
+Future steps would include categorizing each player based on their positions and giving weight to the statistics that would have a better indication of their performance.
+For example, giving more weight to the average number of blocks per game for defensive players.
+Another step would be the incorporation of other models to find better fits, because of the complex relationship between the price and the player statistics, a more sophisticated model may be needed.
 

### 2024-04-24 paper/paper.qmd
compiled results

@@
 
-test_maxey_price_only <- clean_maxey[, -1]
+test_maxey_price_only <- maxey[, -1]
 
@@
 
-test_haliburton_price_only <- clean_haliburton[, -1]
+test_haliburton_price_only <- haliburton[, -1]
 
@@
 
-test_anthony_price_only <- clean_anthony_edward[, -1]
+test_anthony_price_only <- anthony_edward[, -1]
 
@@
 
-## Price of increasing performance
+## Tyrese Maxey Preduction
+```{r}
+#| label: fig-1
+#| fig-cap: The comparision between past season versus predicted improving season
+#| fig-subcap: ["Amount of Power Plays", "Effectiveness of Power Plays"]
+#| echo: false
+#| warning: false
+#| layout-ncol: 2
+
+library(ggplot2)
+
+maxey_prediction_table |> ggplot(aes(x = `Month`, y = `Predicted Price`)) + 
+  geom_line(group =1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Predicted price of future seasons with improving performance",
+    x = "Dates",
+    y = "Price"
+
+  )+ 
+  geom_point() +
+  geom_smooth(method=lm)
+
+price_data |> ggplot(aes(x = `Date`, y = `Tyrese Maxey`)) + 
+  geom_line(group = 1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Predicted price of future seasons with improving performance",
+    x = "Dates",
+    y = "Price"
+
+  )
+
+```
+
+## Tyrese Haliburton Preduction
+```{r}
+#| label: fig-2
+#| fig-cap: The comparision between past season versus predicted improving season
+#| fig-subcap: ["Amount of Power Plays", "Effectiveness of Power Plays"]
+#| echo: false
+#| warning: false
+#| layout-ncol: 2
+
+library(ggplot2)
+
+haliburton_prediction_table |> ggplot(aes(x = `Month`, y = `Predicted Price`)) + 
+  geom_line(group =1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Predicted price of future seasons with improving performance",
+    x = "Dates",
+    y = "Price"
+
+  )+ 
+  geom_point() +
+  geom_smooth(method=lm)
+
+price_data |> ggplot(aes(x = `Date`, y = `Tyrese Haliburton`)) + 
+  geom_line(group = 1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Predicted price of future seasons with improving performance",
+    x = "Dates",
+    y = "Price"
+
+  )
+
+```
+
+## Anthony Edward Prediction
+
+```{r}
+#| label: fig-3
+#| fig-cap: The comparision between past season versus predicted improving season
+#| fig-subcap: ["Amount of Power Plays", "Effectiveness of Power Plays"]
+#| echo: false
+#| warning: false
+#| layout-ncol: 2
+
+library(ggplot2)
+
+anthony_prediction_table |> ggplot(aes(x = `Month`, y = `Predicted Price`)) + 
+  geom_line(group =1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Predicted price of future seasons with improving performance",
+    x = "Dates",
+    y = "Price"
+
+  )+ 
+  geom_point() +
+  geom_smooth(method=lm)
+
+price_data |> ggplot(aes(x = `Date`, y = `Anthony Edward`)) + 
+  geom_line(group = 1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Predicted price of future seasons with improving performance",
+    x = "Dates",
+    y = "Price"
+
+  )
+
+```
 

### 2024-04-25 paper/paper.qmd
touching up

--- 2024-04-24 paper/paper.qmd
@@
 ---
-title: "Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards"
-subtitle: "My subtitle if needed"
+title: "Prizm Silver Rookie Cards"
+subtitle: "An Analysis using statistic performance of a specific player and their rookie card price"
 author: 
@@
 library(readr)
-#write_bib()
 
@@
 
-The first place the data was collected from is ESPN, player statistics were obtained from scrapping the website and picking out the right tables.
+The first place the data was collected from is @ESPN, player statistics were obtained from scrapping the website and picking out the right tables.
 Please be respectful if you decide to use it for any other purpose.
@@
 
-Below is a brief explination of the tables including player statistics:
+Below is a brief explanation of the tables including player statistics:
 
@@
 kable(anthony_edward, padding = 5)
+
 ```
@@
 
-## Price of increasing performance
+## Tyrese Maxey Preduction
+```{r}
+#| label: fig-1
+#| fig-cap: The comparision between past season versus predicted improving season of Tyrese Maxey
+#| fig-subcap: ["Model Predicted Price", "Price from 2022-2024 season"]
+#| echo: false
+#| warning: false
+#| layout-ncol: 2
+
+maxey_prediction_table |> ggplot(aes(x = `Month`, y = `Predicted Price`)) + 
+  geom_line(group =1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Predicted price of future seasons with improving performance",
+    x = "Dates",
+    y = "Price"
+
+  )
+
+price_data |> ggplot(aes(x = `Date`, y = `Tyrese Maxey`)) + 
+  geom_line(group = 1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Price from 2022-2024 season",
+    x = "Dates",
+    y = "Price"
+
+  )
+
+```
+
+## Tyrese Haliburton Preduction
+```{r}
+#| label: fig-2
+#| fig-cap: The comparision between past season versus predicted improving season of Tyrese Haliburton
+#| fig-subcap: ["Model Predicted Price", "Price from 2022-2024 season"]
+#| echo: false
+#| warning: false
+#| layout-ncol: 2
+
+library(ggplot2)
+
+haliburton_prediction_table |> ggplot(aes(x = `Month`, y = `Predicted Price`)) + 
+  geom_line(group =1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Predicted price of future seasons with improving performance",
+    x = "Dates",
+    y = "Price"
+
+  )+ 
+  geom_point() +
+  geom_smooth(method=lm)
+
+price_data |> ggplot(aes(x = `Date`, y = `Tyrese Haliburton`)) + 
+  geom_line(group = 1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Price from 2022-2024 season",
+    x = "Dates",
+    y = "Price"
+
+  )
+
+```
+
+## Anthony Edward Prediction
+
+```{r}
+#| label: fig-3
+#| fig-cap: The comparision between past season versus predicted improving season of Anthony Edward
+#| fig-subcap: ["Model Predicted Price", "Price from 2022-2024 season"]
+#| echo: false
+#| warning: false
+#| layout-ncol: 2
+
+anthony_prediction_table |> ggplot(aes(x = `Month`, y = `Predicted Price`)) + 
+  geom_line(group =1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Predicted price of future seasons with improving performance",
+    x = "Dates",
+    y = "Price"
+
+  )
+
+price_data |> ggplot(aes(x = `Date`, y = `Anthony Edward`)) + 
+  geom_line(group = 1) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
+  labs(
+    title = "Price from 2022-2024 season",
+    x = "Dates",
+    y = "Price"
+
+  )
+
+```
+
+In @fig-1, @fig-2, and @fig-3 the results are all very similar.
+The over all price has a downward trend initially without the use of the model.
+However, in the start of the 2023 season, all three players card price saw an upward trend with then later died down again falling into another downward trend.
+This could be because if people coming back to the sport also bringing more attention to playing cards ultimately leading to increase in the price.
+When the month jumps from April to October, a price increase can be observed, which indicates an end of a season to the start of the next season.
+The predicted price interestingly displayed an increase at the beginning of each season and decreasing of price after around December of each season.
 
@@
 
-## Third discussion point
+## Season timing
+After taking a closer look at trends from both predicted and past data, an interesting point came up mind.
+When observing turning points of the price, they all seems to be the start and end of a season.
+Price increasing trends tends to happen at the start of each season, and then become more and more unpredictable throughout the season.
+This brings attention to the timing of the season and the price may be quite related and even more than the player statistics.
+Because despite implementing an increasing performance for each of the player statistics to run the model on, there are no clear signs of increasing price overall.
+The thing that stood out the most is the price increase at the start of every season in October.
+This could suggest that the initial hype of a new season could be contrbuting to the incresae of the card price.
 
@@
 Sportscardpro only gathers its data from completed transactions of that card on eBay, which is only a portion of the sales that happen on the internet.
-Transactions of the card that often happen offline in stores are also not tracked, if I sold a card to my friend for a cheaper price, it is not reflected in the dataset from Sportscardpro.
+Transactions of the card that often happen offline in stores are also not tracked, if I sold a card to my friend for a cheaper price, it is not reflected in the data set from @Sportscardpro.
 
@@
 ```{r}
-#| include: true
-#| eval: true
+#| label: fig-4
+#| fig-cap: Model fit of Tyrese Maxey
 #| echo: false
-#| message: false
 #| warning: false
+#| layout-ncol: 2
 
@@
   coord_flip()
+```
+```{r}
+#| label: fig-5
+#| fig-cap: Model fit of Tyrese Haliburton
+#| echo: false
+#| warning: false
+#| layout-ncol: 2
 
@@
   coord_flip()
+```
+
+```{r}
+#| label: fig-6
+#| fig-cap: Model fit of Anthony Edward
+#| echo: false
+#| warning: false
+#| layout-ncol: 2
 

### 2024-04-25 paper/paper.qmd
updated read me and fixed citations

@@
 
-The analysis of these three datasets will be carried out using the statistical programming language `R` [@citeR], using the `tidyverse`[@citetidy], `here`[@citehere], and `readxl`[@citexl] packages.
+The analysis of these three datasets will be carried out using the statistical programming language `R` [@citeR], using the `tidyverse`[@tidyverse], `here`[@citehere], and `readxl`[@citexl] packages.
 The figures and tables in the paper are generated using the, respectively, `ggplot2`[@citegg] and `knitr`[@citeknitr] packages.

### 2024-04-25 paper/paper.qmd
final touches

--- 2024-04-25 paper/paper.qmd
@@
 title: "Prizm Silver Rookie Cards"
-subtitle: "An Analysis using statistic performance of a specific player and their rookie card price"
+subtitle: "An Analysis Using Statistic Serformance of an Individual Player and Their Rookie Card Price"
 author: 
@@
 
-The analysis of these three datasets will be carried out using the statistical programming language `R` [@citeR], using the `tidyverse`[@citetidy], `here`[@citehere], and `readxl`[@citexl] packages.
-The figures and tables in the paper are generated using the, respectively, `ggplot2`[@citegg] and `knitr`[@citeknitr] packages.
+The analysis of these three data sets will be carried out using the statistical programming language `R` [@citeR], using the `here`[@R-here], and `readxl`[@citexl] packages.
+Various packages were used throughout the writing of this paper including `tidyverse` [@tidyverse], `arrow` [@arrow], `here` [@here], `ggmap` [@ggmap], `knitr` [@knitr], `dplyr` [@dplyr], `janitor` [@janitor], `lintr` [@lintr], and `rstanarm` [@rstanarm].
 
@@
 ## Confounding variables
-The linear model may be too simple due to each player's positions and playstyles.
+The linear model may be too simple due to each player's positions and play styles.
 Because we are assuming that the higher the statistics are the better a player is performing.
@@
 If a player is known and in charge of defensive plays, their blocks and rebounds may be more important compared to attack-oriented players.
+The mock data had in increase of 2% each month of each players statistics, which should lead to overall increase of the price if the statistics were all positively related to the price.
+The weight of an varibale might be overlooked or underlooked which could be casuing this issue.
+
 The behavior of a player outside the league is also very crucial in terms of this.
-Even though Ja Morant played well in the league, he had multiple occasions where he displayed illegal objects during his livestream on Instagram.
+Even though Ja Morant played well in the league, he had multiple occasions where he displayed illegal objects during his live stream on Instagram.
 This devastated his reputation overall and he also received game restrictions as punishment.
@@
 
-## Season timing
+## Time and Price
+
+The time frame also plays a crucial role in prices of many items in our every day life.
+For example, the rent price in Toronto starting May is lower compared to September from my past experience.
+This is due to the mass fluctuation of students leaving Toronto in May and coming back to Toronto in September.
+Timing and price in this case also plays a role in the change or card prices.
+
 After taking a closer look at trends from both predicted and past data, an interesting point came up mind.
@@
 The thing that stood out the most is the price increase at the start of every season in October.
-This could suggest that the initial hype of a new season could be contrbuting to the incresae of the card price.
+This could suggest that the initial hype of a new season could be contrbuting to the increase of the card price.
 
@@
 For example, giving more weight to the average number of blocks per game for defensive players.
+Upon taking a look at @fig-4, @fig-5, and @fig-6, the fit of the data are not very good.
 Another step would be the incorporation of other models to find better fits, because of the complex relationship between the price and the player statistics, a more sophisticated model may be needed.
+I think also using an average of all the player's statistics and price data and compare them to individual model would also be something beneficial, exploring the overall relationship rather than one at a time.
+Overall, this analysis gives insgitht to how complex the relationship is and that a lot more work would be required to be done.
 

### 2024-04-25 paper/paper.qmd
fix cross refference issue

@@
 The thing that stood out the most is the price increase at the start of every season in October.
-This could suggest that the initial hype of a new season could be contrbuting to the increase of the card price.
+This could suggest that the initial hype of a new season could be contributing to the increase of the card price.
 
@@
 For example, giving more weight to the average number of blocks per game for defensive players.
-Upon taking a look at @fig-4, @fig-5, and @fig-6, the fit of the data are not very good.
+Upon taking a look at @sec-modelcheck, the fit of the data are not very good.
 Another step would be the incorporation of other models to find better fits, because of the complex relationship between the price and the player statistics, a more sophisticated model may be needed.
@@
 
-## Model Check
+## Model Check {#sec-modelcheck}
 
